### 2014-08-03 Pero_Transcriptome.tex
update
added transcoder stats

I then estimated gene expression on each of these tissue-specific datasets, which allowed me to understand expression patterns in the multiple tissues {\hypertarget{Figure 1}{Figure 1}}.

@@

After expression estimation, the filtered assemblies were concatenated together, and after removal of redundancy with cd-hit-est, 123,123 putative transcripts remained. From this filtered concatenated dataset, I extracted 64355 putative coding sequences (60Mb). Of these 64355 sequences, 37960 were complete exons (containing both start and stop codons), while other were either truncated at the 5-prime end (16880 sequences), 3-prime end (4203 sequences), or were internal (5312 sequencing having neither stop nor start codon).

>>>>

@@

I then estimated gene expression on each of these tissue-specific datasets, which allowed me to understand expression patterns in the multiple tissues {\hypertarget{Figure 1}{Figure 1}}. After expression estimation, the filtered assemblies were concatenated together, and after removal of redundancy with cd-hit-est, 123,123 putative transcripts remained. From this filtered concatenated dataset, I extracted 71626 putative coding sequences (72Mb). Of these 71626 sequences, 38221 were complete exons (containing both start and stop codons), while other were either truncated at the 5-prime end (20239 sequences), 3-prime end (6445 sequences), or were internal (6721 sequencing having neither stop nor start codon).
